Online analysis supplement

### 2021-11-08 index.Rmd
Add new timeseries plot

>>>>

### Multiple lines

Here we create two plots. One to show all main variables' time trends for each region, and country within region. Then, show the outcome time trends for top internet trend in each region.

```{r}
pa <- bind_rows(
  gbd %>% 
    group_by(region, country, year, cause) %>% 
    summarise(mean = mean(val/100)),
  itu %>% 
    group_by(region, country, year) %>% 
    summarise(mean = mean(internet, na.rm = TRUE)) %>% 
    mutate(cause = "Internet")
) %>% 
  ungroup() %>% 
  mutate(cause = fct_relevel(cause, "Internet")) %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean, color = cause)) +
  scale_color_brewer(
    "Variable",
    palette = "Set1", direction = -1
  ) +
  scale_y_continuous(
    "Rate",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(aes(group = interaction(country, cause)), alpha = .25, size = .4) +
  stat_summary(fun = mean, geom = "line", size = .6) +
  facet_grid(cause~region, scales = "free_y") +
  theme(legend.position = "none")

# Get top 1 internet trend country in each region
top_trends <- gbd %>% 
  semi_join(distinct(itu, country)) %>% 
  group_by(region, country) %>% 
  summarise(tidy(lm(internet ~ time, data = cur_data_all()))) %>% 
  filter(term == "time") %>% 
  group_by(region) %>% 
  slice_max(order_by = estimate, n = 1)
pb <- gbd %>% 
  filter(country %in% top_trends$country) %>%
  mutate(country = factor(country, levels = top_trends$country)) %>% 
  mutate(Group = str_glue("{sex} ({age})")) %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, val/100, col = Group)) +
  scale_color_brewer(palette = "Paired") +
  scale_y_continuous(
    "Rate",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  stat_summary(fun = mean, geom = "line", size = .6) +
  facet_grid(cause~country, scales = "free_y")

(pa + theme(axis.title.x = element_blank())) / 
  pb * 
  theme(panel.spacing = unit(2, "pt")) +
  plot_layout(heights = c(4, 3)) +
  plot_annotation(tag_levels = "A")
ggsave(
  "output/Fig-all-vars-timeseries.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```
